Run aquaculture model for Atlantic salmon

### 2025-10-21 05_formulating_feeds.qmd
Bit of cleanup

ingred_inputs_file <- file.path(input_feed_profile_path, "all_ingredients.csv")
feed_input_file <- file.path(input_feed_profile_path, "all_feeds.xlsx")
```

@@

ingreds <- ingred_inputs_file %>% 
  read.csv() %>% 
  mutate(ingredient = as.factor(ingredient))
ingred_nms <- levels(ingreds$ingredient)
```

@@

>>>>

ingred_inputs_file <- file.path(input_feed_profile_path, "all_ingredients.xlsx")
feed_input_file <- file.path(input_feed_profile_path, "all_feeds.xlsx")
```

@@

ingreds <- ingred_inputs_file %>% 
  read_excel(sheet = "all_ingredients") %>% 
  mutate(ingredient = as.factor(ingredient))
ingred_nms <- levels(ingreds$ingredient)
```

@@

```{r}

```

### 2025-10-21 06_run_atlantic_salmon_model.qmd
Bit of cleanup

# Run results
targets::tar_make(
  names = c("farm_run_chunked", "stat_names", "farm_results_chunked", "biomass_produced_chunked", "cohort_results_chunked" ), 
  seconds_meta_append = 90,
  shortcut = T
)

>>>>

# Run results
targets::tar_make(
  names = c("farm_run_chunked", "stat_names", "farm_results_chunked", "biomass_produced_chunked", "cohort_results_chunked" ), 
  seconds_meta_append = 90,
  shortcut = T # only if you've done the pre-run
)
